### 2021-03-18 README.Rmd
moved API Key section inside the installation instruction

## Requesting an AIMS Data Platform API Key

@@

The API Key can be passed to the package functions as an additional
`api_key = "XXXX"` argument. alternatively, the environment variable
`AIMS_DATAPLATFORM_API_KEY` can be stored in the user's `.Renviron` file for
automatic loading at the start of an R session. In that case the users can 
modify their `.Renviron` file by adding the following line:

@@

At this stage `dataaimsr` is not hosted on CRAN R package network.
An alternative method of installation is to use the R `remotes` package.

R `remotes` can be installed using the following command:

>>>>

### Requesting an AIMS Data Platform API Key

@@

The API Key can be passed to the package functions as an additional
`api_key = "XXXX"` argument. **However**, we strongly encourage users to
maintain their API key as a private locally hidden environment variable
(`AIMS_DATAPLATFORM_API_KEY`) in the `.Renviron` file for
automatic loading at the start of an R session. Please read this
[article](https://CRAN.R-project.org/package=httr/vignettes/secrets.html)
which details why keeping your API private is extremely important.

Users can modify their `.Renviron` file by adding the following line:

@@

### Package

At this stage `dataaimsr` is not hosted on CRAN R package network, although
we re aiming to submit it there very soon. For the moment, an alternative
method of installation is to use the R `remotes` package. R `remotes` can be
installed using the following command:
